%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Duy Nguyen} \\ \vspace{1pt}
     \href{mailto:dnguyen122003@gmail.com}{\underline{dnguyen122003@gmail.com}} $|$ 
    \href{https://linkedin.com/in/duy---nguyen}{\underline{linkedin.com/in/duy---nguyen/}} $|$
    \href{https://github.com/jerry-ng2}{\underline{github.com/jerry-ng2}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Massachusetts - Lowell | Lowell, MA}{Aug. 2022 - May 2026}
      {Bachelor of Science in Computer Science with a focus in Data Science}{Aug. 2022 -- May 2026}
      \small{\item{
    {Bachelor of Science in Computer Science with a focus in Data Science, Math Minor}}}

    \small{\item{
    \textbf{Academic Achievements}{: Dean's list: 2022-2024, UML Faculty and Staff Scholarship, UML Powerlifting Club Member}}}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, JavaScript, HTML/CSS, XML, SQL, YML} \\
     \textbf{OS/Applications}{: ExpressJS, PostgreSQL, ReactJS, NodeJS, Fedora, Ubuntu, Windows, MacOS, PyTorch, TensorFlow, Apache Spark, Hadoop, Ansible} \\
     \textbf{Developer Tools}{: GCC, GDB, Git, Github, Make, Valgrind, VS Code, Visual Studio, VIM} \\
    }}
 \end{itemize}


%-------------------------------------------





%-----------EXPERIENCE-----------
\section{Experiences}
  \resumeSubHeadingListStart

      \resumeSubheading
      {A\&R Intern - indify $|$ \textit{New York, NY}}
      { June 2024 - September 2024}
      {indify}{New York , NY}
    \resumeItemListStart
        \resumeItem{Facilitate artist discovery via manipulating social algorithms to identify artists with traction.}
        \resumeItem{Organized meetings between artists, management, and team members, building relationships that led to 10+ successful partnerships.}
        \resumeItem{Help source 200+ artists as potential clients and created database entries that contained info of each artists.}
        \resumeItem{Increased independent artists funding and strategic value by 20\%.}
        \resumeItem{Created meaningful relationships with clients to understand what resources they need to scale their businesses.}
    \resumeItemListEnd

    \resumeSubheading
      {Lab Assistant/Tutor - UML $|$ \textit{Lowell, MA}}{August 2022 -- Present}
      {UMASS Lowell - Miner School of CIS}{Lowell, MA}
      \resumeItemListStart
        \resumeItem{Developed images for UMASS Lowell computer labs of 30+ machines using FOG and Clonezilla reducing deployment time by 40\%.}
        \resumeItem{Automated lab management tasks with Ansible Playbook, decreasing manual lab changes by 50\%.}
        \resumeItem{Managed multiple computer labs for students and faculty to use for work, research, etc.}
        \resumeItem{Tutored 50+ students, helping them excel in introductory computer science courses.}
        \resumeItem{Collaborated in seeting up and managing data servers for UMASS Lowell.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
    {Freelance Web Developer - Contract Based $|$ \textit{Lowell, MA}}{November 2023 - May 2024}
    {Project Based Contract}{Lowell, MA}
    \resumeItemListStart
        \resumeItem{Conversion of DOS based application to Web UI.}
        \resumeItem{Developed a RESTful API using ExpressJS to create  queries into a PostgreSQL database.}
        \resumeItem{Utilized React to develop the apps in HTML/CSS and JavaScript.}
        \resumeItem{Implement security features to the development app.}
        


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Machine Learning} $|$  \textbf{Researcher} $|$ \emph{Apache Spark, Hadoop, PySpark, Jupyter Notebook}}
          {}
          \resumeItemListStart
            \resumeItem{Researched how machine learning frameworks function.}
            \resumeItem{Created a Hadoop cluster of 30 machines.}
            \resumeItem{Tested the cluster using MapReduced python and java programs.}
            \resumeItem{Implemented Apache Spark to distribute work load amongst various machines.}
            \resumeItem{Experimented with panda dataframes to optimize the training time of preexisting models.}
          \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Customer Info Website} $|$ \textbf{Full Stack Engineer} $|$ \emph{PostgrSQL, Express.js, React.js, Node.js, JavaScript}}{}
            \resumeItemListStart
                \resumeItem{Created a website that is able to query customer information into a database.}
                \resumeItem{Hid the database behind a login page using bcrypt encryption.}
                \resumeItem{Created multiple databases to store different data and login information.}
                \resumeItem{Implemented Express.js as a RESTful API as a backend.}
            \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CS Account Form} $|$  \textbf{Web Developer} $|$ \emph{Firebase, HTML/CSS, React, Python, Flask}}{}
          \resumeItemListStart
            \resumeItem{Worked with a team to develop a full-stack sign up form.}
            \resumeItem{Implemented Flask serving as a REST API with React as the frontend.}
            \resumeItem{Implemented Firebase to store user responses and keep track of user's data.}
            \resumeItem{Worked with a team to deploy the web application using NGINX.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
\end{document}